Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-01-14 paper/reviewers-response.Rmd

> "Overall I found the paper well-written and sound, but there were a few questions I had that could improve clarity in the methods used. In the glm that used nD as the response variable, is there any concern that including N (number of species) as a predictor may cause a problem when the response is D/N? I can understand why this was included, but I can also imagine this resulting in models that show an effect of N when there is none (I could be wrong on this)."

Thanks for the observation. As you mention, we believe it is ok to include the sample size as a predictor in this model for three reasons. First, there are several instances when the probability of something occurring increases or decreases with sampling effort, etc. It *does* imply a non-linear relationship though. Second, if there were a relationship between N on D, then using D/N (as opposed to of D) as the response variable and N as a predictor would actually reduce the size of the effect of N, rather than amplify it. If on the other hand, N and D are completely decoupled, then using D/N as the response variable should affect the intercept but not the coefficient of D. Third, in any case we only found a comparatively small effect of N on D. Although it might be relevant statistically it seems to be ecologically insignificant. 
<!-- FDO: Daniel, could you please double check this makes sense? -->

> "In the species level glm, it was not entirely clear if models were fit to each network individually or if all species were lumped together (the former is what I think was done based on my reading of the text). Regardless I wonder if it would change the results if a mixed effects model was fit to lumped data, using network as a random effect."

*Accepted and changed*: We are sorry for the confusion. In the species level GLM, we lumped all species from different networks together. We have modified the text in \lr{M-R2-one-lumped-model-a} and \lr{M-R2-one-lumped-model-b} to make this clearer. Moreover, we actually did test for random effects in the model. We tested random effects that allowed for a random intercept for the network (but also its site, and the study it comes from). In all cases, the variance among groups was zero. This means that likely there are no differences on the distribution of control capacity between networks (or site and study) and therefore it was unnecessary to include random effects in the models presented in the paper. We have corrected this omission and describe the random effects in \lr{M-R2-random-effects}.
<!-- DBS: I don't think that "possible variation across communities" (which is the text in the paper) is specific enough to say what the random effects actually would have been. -->
<!-- FDO: I have reworded to 'We initially included random effects to account for possible variation across communities, but we found that the among-group variance was effectively zero, and therefore random effects were not included in further analyses'. Is that what you mean? -->

### 2019-01-14 paper/reviewers-response.Rmd

> "*L405*: 'central in their community'"

*Accepted and changed*: We've changed the wording to avoid ambiguity. Now the text reads "...to attain high centrality in their communities..." (\lr{M-R2-central-in-their-communities}).

> "*L406*: 'inherently different. The sentence spanning lines 407-410 is quite confusing  - please clarify.

*Accepted and changed*: We rephrased this sentences as follows: "We found that it is not that invasive plants have some different mechanism for influencing the community compared to their native counterparts. Both native species and invasive plants tended to attain a high control capacity if they were important to network persistence, were abundant, and depended little on other species" \lr{M-R2-inherrently-different}.

@@

> "*L430*: 'marginally affected by the topology of their interactions'"

*Accepted and changed*: We have rephrased this line as: "By accounting for network dynamics (even if in a simple way), structural stability incorporates more ecological realism, especially in the extreme scenario in which the structure of interactions within the community only marginally affects the community's state" (\lr{M-R2-marginally-affected}).

### 2019-01-14 paper/manuscript.Rmd
Improve explanation about candidates in species models
Correcting quoting mistakes in the response to reviewers

\R{R2-one-lumped-model-a}We then examined how species-level properties were related to control capacity using a set of candidate generalised linear models with binomial error structure. 
These models included five predictor variables that mirror the network-level predictors. 
First, the species' contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
Second,\R{R2-species-strength-a} the species' strength (the sum of a species' visits), which quantifies the strength of a species' associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
Third, the direction of asymmetry which quantifies the net balance in dependencies; that is, it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007]. 
Fourth, the species' degree in order to account for the intrinsic centrality of a species.
Finally, we included a categorical variable for the species' trophic level (plant or pollinator) and an interaction term between trophic level and the previous four variables. 
To facilitate comparison between predictors, degree and visitation strength were log-transformed and all four continuous variables were scaled to have a mean of zero and a standard deviation of one. 
\R{R2-one-lumped-model-b}In these models, species from all networks were analysed together. 
\R{R2-random-effects}We initially included random effects to account for possible variation across communities, but we found that the among-group variance was effectively zero, and therefore random effects were not included in further analyses. 
\R{R2-all-candidates}We then generated all possible candidate models.
To identify the models that were best supported by the data, we first determined the most parsimonious random structure using the AICc. 
The relative importance of variables was then assessed by looking at their effect sizes in the top-ranked models and the cumulative weight of the models in which they are present.

@@

Our choice of studying invaded/uninvaded networks was based on a desire to contrast the extensive empirical evidence of the role of invasive plants with our theoretical results. 
We found that invasive plants were always critical for network control and as such our results were in line with our expectations. 
Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; @bartomeus_contrasting_2008; @henriksson_strong_2016] \R{R2-central-in-their-communities}and to attain high centrality in their communities [@vila_invasive_2009; @palacio_generalist_2016]. 
\R{R2-inherrently-different} We found, however, that it is not that invasive plants have some different mechanism for influencing the community compared to their native counterparts [@emer_species_2016; @stouffer_how_2014]. 
Both native species and invasive plants tended to attain a high control capacity if they were important to network persistence, were abundant, and depended little on other species. 
Furthermore, our observation that changes in the abundance of invasive plants (and presumably all critical species) are crucial to modify the state of the community agrees with recent evidence showing that ecosystem restoration focused on the eradication of invasive plants can have transformative desirable effects in plant-pollinator communities [@kaiser-bunbury_ecosystem_2017]. 
However, our results also suggest that removals must be exercised with caution. 
Not only it is hard to predict the direction in which the system will change, but we also show that critical species can underpin the coexistence of species and therefore some communities may be acutely vulnerable to their eradication [@traveset_invaders_2013; @albrecht_consequences_2014].

>>>>

\R{R2-one-lumped-model-a}We then examined how species-level properties were related to control capacity using a set of candidate generalised linear models with binomial error structure. 
These models included five predictor variables that mirror the network-level predictors. 
First, the species' contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
Second,\R{R2-species-strength-a} the species' strength (the sum of a species' visits), which quantifies the strength of a species' associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
Third, the direction of asymmetry which quantifies the net balance in dependencies; that is, it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007]. 
Fourth, the species' degree in order to account for the intrinsic centrality of a species.
Finally, we included a categorical variable for the species' trophic level (plant or pollinator) and an interaction term between trophic level and the previous four variables. 
To facilitate comparison between predictors, degree and visitation strength were log-transformed and all four continuous variables were scaled to have a mean of zero and a standard deviation of one. 
\R{R2-one-lumped-model-b}In these models, species from all networks were analysed together. 
\R{R2-random-effects}We initially included random effects to account for possible variation across communities, but we found that the among-group variance was effectively zero, and therefore random effects were not included in further analyses. 
\R{R2-all-candidates}We then generated all possible candidate models across the space of models with all, some, and none of the predictor variables.
To identify the models that were best supported by the data, we first determined the most parsimonious random structure using the AICc. 
The relative importance of variables was then assessed by looking at their effect sizes in the top-ranked models and the cumulative weight of the models in which they are present.

@@

Our choice of studying invaded/uninvaded networks was based on a desire to contrast the extensive empirical evidence of the role of invasive plants with our theoretical results. 
We found that invasive plants were always critical for network control and as such our results were in line with our expectations. 
Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; @bartomeus_contrasting_2008; @henriksson_strong_2016] \R{R2-central-in-their-communities}and to attain high centrality in their communities [@vila_invasive_2009; @palacio_generalist_2016]. 
We found, however, that it is not that invasive plants have some \R{R2-inherrently-different} different mechanism for influencing the community compared to their native counterparts [@emer_species_2016; @stouffer_how_2014]. 
Both native species and invasive plants tended to attain a high control capacity if they were important to network persistence, were abundant, and depended little on other species. 
Furthermore, our observation that changes in the abundance of invasive plants (and presumably all critical species) are crucial to modify the state of the community agrees with recent evidence showing that ecosystem restoration focused on the eradication of invasive plants can have transformative desirable effects in plant-pollinator communities [@kaiser-bunbury_ecosystem_2017]. 
However, our results also suggest that removals must be exercised with caution. 
Not only it is hard to predict the direction in which the system will change, but we also show that critical species can underpin the coexistence of species and therefore some communities may be acutely vulnerable to their eradication [@traveset_invaders_2013; @albrecht_consequences_2014].
